---
title: "Chennai Covid Impacted Streets"
output: 
  html_document:
    css: /home/arunkumar/Documents/GitHub/aruncps.github.io/assets/css/main.css
    includes:
       in_header: GA_Script.html
---
* **Source:** [Data from Chennai Corporation](http://covid19.chennaicorporation.gov.in/covid/positivecases)
* **Latest data import date:** `r format(Sys.time()-100000, '%d %B, %Y')`
* **Summary:** Chennai Corp. publishes COVID cases by street level. Using it, heatmap is generated to view the number of streets impacted in each Zone by Area.
* **Disclaimer:** No corrections were applied to fix the typos. *Known Issues: 1. Spelling mistakes, 2. Zone mismatches*
* **Inspired from:** Daily posting by [Prof Shamika Ravi](https://twitter.com/ShamikaRavi) from Jan'2020

## List of Zones: {#loz}
  + [All Zones](#anchor00)
  + [Zone 1 - Thiruvottiyur](#anchor01)
  + [Zone 2 - Manali](#anchor02)
  + [Zone 3 - Madhavaram](#anchor03)
  + [Zone 4 - Tondiarpet](#anchor04)
  + [Zone 5 - Royapuram](#anchor05)
  + [Zone 6 - Thiru. Vi. Ka. Nagar](#anchor06)
  + [Zone 7 - Ambattur](#anchor07)
  + [Zone 8 - Anna Nagar](#anchor08)
  + [Zone 9 - Teynampet](#anchor09)
  + [Zone 10 - Kodambakkam](#anchor10)
  + [Zone 11 - Valasaravakkam](#anchor11)
  + [Zone 12 - Alandur](#anchor12)
  + [Zone 13 - Adyar](#anchor13)
  + [Zone 14 - Perungudi](#anchor14)
  + [Zone 15 - Sholinganallur](#anchor15)

```{r packages, results="hide",echo=FALSE, message=FALSE, warning=FALSE}
#------- Packages
lapply(c("tidyverse","rvest","hrbrthemes","viridis","plotly","scales","stringr","zoo","tidyquant"), library, character.only = TRUE)
#------- Zone Dictionary
Zone <- data.frame(Zone = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15),
                 ZoneName = c("Zone 01 - Thiruvottiyur","Zone 02 - Manali"
                              ,"Zone 03 - Madhavaram","Zone 04 - Tondiarpet"
                              ,"Zone 05 - Royapuram","Zone 06 - Thiru. Vi. Ka. Nagar"
                              ,"Zone 07 - Ambattur","Zone 08 - Anna Nagar"
                              ,"Zone 09 - Teynampet","Zone 10 - Kodambakkam"
                              ,"Zone 11 - Valasaravakkam","Zone 12 - Alandur"
                              ,"Zone 13 - Adyar","Zone 14 - Perungudi"
                              ,"Zone 15 - Sholinganallur")
                    )
#------- Import CSV
Chennai_covid_data<-read.table("/home/arunkumar/Documents/GitHub/ChennaiCovid/data_covid.csv",header=TRUE, row.names=NULL)
Chennai_covid_data<-tibble(Chennai_covid_data)
Chennai_covid_data<- Chennai_covid_data %>% mutate(Area=str_to_title(Area))

#------- Zone level Dataframe
All_Chennai_covid_data<-Chennai_covid_data %>% 
  group_by(importDate) %>% 
  summarize(
    impactedStreets=length(Street),
    countOfCases=sum(Cases)
  )

#------- Zone level Dataframe
Zone_Chennai_covid_data<-Chennai_covid_data %>% 
  group_by(importDate,Zone) %>% 
  summarize(
    impactedStreets=length(Street),
    countOfCases=sum(Cases)
  )
Zone_Chennai_covid_data<- Zone_Chennai_covid_data %>% inner_join(Zone, by = c("Zone"="Zone"))

#------- Area level Dataframe
Area_Chennai_covid_data<-Chennai_covid_data %>% 
  group_by(importDate,Zone,Area) %>% 
  summarize(
    impactedStreets=length(Street),
    countOfCases=sum(Cases)
  )

```

## All Zones {#anchor00}
```{r echo=FALSE, warning=FALSE, fig.height=3, fig.width=7}
All_Chennai_covid_data <- All_Chennai_covid_data %>% ungroup()
All_Chennai_covid_data$importDate<-as.Date(as.character(All_Chennai_covid_data$importDate))

ggplot(All_Chennai_covid_data,aes(importDate, impactedStreets,fill=impactedStreets)) +
  geom_bar(stat="identity", color="white", fill="#e3e3e3") +
  geom_line(aes(importDate, impactedStreets), linetype=2, size=.3, color="black") +
  geom_ma(ma_fun = EMA, n = 7, linetype=1, color="blue") + 
  scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  theme_classic() +
  xlab(label = "Date") +
  theme(strip.placement = "outside",
        plot.title = element_text(hjust = 0.5),
        axis.title.y = element_blank(), # Remove y-axis title
        strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        legend.position="top",
        panel.spacing.x = unit(4, "mm")
  ) +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m") +
  scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
  labs(subtitle = "7-day moving average") + theme(plot.subtitle=element_text(size=8, color="blue"))

```

```{r echo=FALSE, warning=FALSE, fig.height=6, fig.width=7}
Zone0_Chennai_covid_data <- Zone_Chennai_covid_data %>% ungroup()
Zone0_Chennai_covid_data$importDate<-as.Date(as.character(Zone0_Chennai_covid_data$importDate))

ggplot(Zone0_Chennai_covid_data
       ,aes(importDate, ZoneName, fill= impactedStreets)) + 
  geom_tile(colour="white",size=0.25) +
  scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  ylab(label = "Area") +
  xlab(label = "Date") +
  scale_y_discrete(limits = rev(levels(as.factor(droplevels(Zone0_Chennai_covid_data$ZoneName) ))) 
                   ,position = "left") +
  theme_classic() +
  theme(strip.placement = "outside",
        plot.title = element_text(hjust = 0.5),
        axis.title.y = element_blank(), # Remove y-axis title
        strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        legend.position="top"
  ) +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m")

```

```{r echo=FALSE, warning=FALSE, fig.height=8, fig.width=7}
ggplot(Zone0_Chennai_covid_data,aes(importDate, impactedStreets,fill=impactedStreets)) +
  geom_bar(stat="identity", color="white", fill="#e3e3e3") +
  geom_line(aes(importDate, impactedStreets), linetype=2, size=.3, color="black") +
  geom_ma(ma_fun = EMA, n = 7, linetype=1, color="blue") + 
  scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  theme_classic() +
  xlab(label = "Date") +
  theme(strip.placement = "outside",
        plot.title = element_text(hjust = 0.5),
        axis.title.y = element_blank(), # Remove y-axis title
        strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        legend.position="top",
        panel.spacing.x = unit(4, "mm")
  ) +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m") +
  facet_wrap(~ ZoneName, scales = "free_x", ncol = 3) +
  labs(subtitle = "7-day moving average") + theme(plot.subtitle=element_text(size=8, color="blue"))
```

###### [Back to full list of Zones](#loz) {style="float:right"}

## Zone 1 - Thiruvottiyur {#anchor01}
```{r echo=FALSE, warning=FALSE}
Zone1_Chennai_covid_data <- Area_Chennai_covid_data %>%filter(Zone %in% c(1) ) %>% ungroup()
Zone1_Chennai_covid_data$importDate<-as.Date(as.character(Zone1_Chennai_covid_data$importDate))

ggplot(Zone1_Chennai_covid_data
       ,aes(importDate, Area, fill= impactedStreets)) + 
  geom_tile(colour="white",size=0.25) +
  facet_grid(switch = "y", scales = "free_y", space = "free_y") +
  scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  ylab(label = "Area") +
  xlab(label = "Date") +
  scale_y_discrete(limits = rev(levels(as.factor(Zone1_Chennai_covid_data$Area))) ) +
  theme_classic() +
  theme(strip.placement = "outside",
          plot.title = element_text(hjust = 0.5),
          axis.title.y = element_blank(), # Remove y-axis title
          strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
          legend.position="top"
      ) +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m")

```

```{r echo=FALSE, warning=FALSE, message=FALSE, fig.height=7, fig.width=7}
ggplot(Zone1_Chennai_covid_data,aes(importDate, impactedStreets,fill=impactedStreets)) +
  geom_bar(stat="identity", color="white", fill="#e3e3e3") +
  geom_line(aes(importDate, impactedStreets), linetype=2, size=.3, color="black") +
  geom_ma(ma_fun = EMA, n = 7, linetype=1, color="blue") +
  scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  theme_classic() +
  xlab(label = "Date") +
  theme(strip.placement = "outside",
        plot.title = element_text(hjust = 0.5),
        axis.title.y = element_blank(), # Remove y-axis title
        strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        legend.position="top",
        panel.spacing.x = unit(4, "mm")
  ) +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m") +
  facet_wrap(~ Area, scales = "free_x", ncol = 3) +
  labs(subtitle = "7-day moving average") + theme(plot.subtitle=element_text(size=8, color="blue"))

```

###### [Back to full list of Zones](#loz) {style="float:right"}

## Zone 2 - Manali {#anchor02}
```{r echo=FALSE, warning=FALSE}
Zone2_Chennai_covid_data <- Area_Chennai_covid_data %>%filter(Zone %in% c(2) ) %>% ungroup()
Zone2_Chennai_covid_data$importDate<-as.Date(as.character(Zone2_Chennai_covid_data$importDate))

ggplot(Zone2_Chennai_covid_data
       ,aes(importDate, Area, fill= impactedStreets)) + 
  geom_tile(colour="white",size=0.25) +
  facet_grid(switch = "y", scales = "free_y", space = "free_y") +
  scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  ylab(label = "Area") +
  xlab(label = "Date") +
  scale_y_discrete(limits = rev(levels(as.factor(Zone2_Chennai_covid_data$Area) )) ) +
  theme_classic() +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m") +
  theme(strip.placement = "outside",
          plot.title = element_text(hjust = 0.5),
          axis.title.y = element_blank(), # Remove y-axis title
          strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
          legend.position="top"
      )

```
```{r echo=FALSE, warning=FALSE, message=FALSE, fig.height=7, fig.width=7}
ggplot(Zone2_Chennai_covid_data,aes(importDate, impactedStreets,fill=impactedStreets)) +
  geom_bar(stat="identity", color="white", fill="#e3e3e3") +
  geom_line(aes(importDate, impactedStreets), linetype=2, size=.3, color="black") +
  geom_ma(ma_fun = EMA, n = 7, linetype=1, color="blue") +
  scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  theme_classic() +
  xlab(label = "Date") +
  theme(strip.placement = "outside",
        plot.title = element_text(hjust = 0.5),
        axis.title.y = element_blank(), # Remove y-axis title
        strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        legend.position="top",
        panel.spacing.x = unit(4, "mm")
  ) +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m") +
  facet_wrap(~ Area, scales = "free_x", ncol = 3) +
  labs(subtitle = "7-day moving average") + theme(plot.subtitle=element_text(size=8, color="blue"))
```

###### [Back to full list of Zones](#loz) {style="float:right"}

## Zone 3 - Madhavaram {#anchor03}
```{r echo=FALSE, warning=FALSE}
Zone03_Chennai_covid_data <- Area_Chennai_covid_data %>%filter(Zone %in% c(3) ) %>% ungroup()
Zone03_Chennai_covid_data$importDate<-as.Date(as.character(Zone03_Chennai_covid_data$importDate))

ggplot(Zone03_Chennai_covid_data
       ,aes(importDate, Area, fill= impactedStreets)) + 
  geom_tile(colour="white",size=0.25) +
  facet_grid(switch = "y", scales = "free_y", space = "free_y") +
  scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  ylab(label = "Area") +
  xlab(label = "Date") +
  scale_y_discrete(limits = rev(levels(as.factor(Zone03_Chennai_covid_data$Area ))) ) +
  theme_classic() +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m") +
  theme(strip.placement = "outside",
          plot.title = element_text(hjust = 0.5),
          axis.title.y = element_blank(), # Remove y-axis title
          strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
          legend.position="top"
      )

```
```{r echo=FALSE, warning=FALSE, message=FALSE, fig.height=7, fig.width=7}
ggplot(Zone03_Chennai_covid_data,aes(importDate, impactedStreets,fill=impactedStreets)) +
  geom_bar(stat="identity", color="white", fill="#e3e3e3") +
  geom_line(aes(importDate, impactedStreets), linetype=2, size=.3, color="black") +
  geom_ma(ma_fun = EMA, n = 7, linetype=1, color="blue") +  
  scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  theme_classic() +
  xlab(label = "Date") +
  theme(strip.placement = "outside",
        plot.title = element_text(hjust = 0.5),
        axis.title.y = element_blank(), # Remove y-axis title
        strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        legend.position="top",
        panel.spacing.x = unit(4, "mm")
  ) +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m") +
  facet_wrap(~ Area, scales = "free_x", ncol = 3) +
  labs(subtitle = "7-day moving average") + theme(plot.subtitle=element_text(size=8, color="blue"))

```

###### [Back to full list of Zones](#loz) {style="float:right"}

## Zone 4 - Tondiarpet {#anchor04}
```{r echo=FALSE, warning=FALSE}
Zone04_Chennai_covid_data <- Area_Chennai_covid_data %>%filter(Zone %in% c(4) ) %>% ungroup()
Zone04_Chennai_covid_data$importDate<-as.Date(as.character(Zone04_Chennai_covid_data$importDate))

ggplot(Zone04_Chennai_covid_data
       ,aes(importDate, Area, fill= impactedStreets)) + 
  geom_tile(colour="white",size=0.25) +
  facet_grid(switch = "y", scales = "free_y", space = "free_y") +
  scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  ylab(label = "Area") +
  xlab(label = "Date") +
  scale_y_discrete(limits = rev(levels(as.factor(Zone04_Chennai_covid_data$Area ))) ) +
  theme_classic() +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m") +
  theme(strip.placement = "outside",
          plot.title = element_text(hjust = 0.5),
          axis.title.y = element_blank(), # Remove y-axis title
          strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
          legend.position="top"
      )

```
```{r echo=FALSE, warning=FALSE, message=FALSE, fig.height=7, fig.width=7}
ggplot(Zone04_Chennai_covid_data,aes(importDate, impactedStreets,fill=impactedStreets)) +
  geom_bar(stat="identity", color="white", fill="#e3e3e3") +
  geom_line(aes(importDate, impactedStreets), linetype=2, size=.3, color="black") +
  geom_ma(ma_fun = EMA, n = 7, linetype=1, color="blue") +  
  scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  theme_classic() +
  xlab(label = "Date") +
  theme(strip.placement = "outside",
        plot.title = element_text(hjust = 0.5),
        axis.title.y = element_blank(), # Remove y-axis title
        strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        legend.position="top",
        panel.spacing.x = unit(4, "mm")
  ) +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m") +
  facet_wrap(~ Area, scales = "free_x", ncol = 3) +
  labs(subtitle = "7-day moving average") + theme(plot.subtitle=element_text(size=8, color="blue"))

```

###### [Back to full list of Zones](#loz) {style="float:right"}

## Zone 5 - Royapuram  {#anchor05}
```{r echo=FALSE, warning=FALSE, fig.height=7, fig.width=7}
Zone05_Chennai_covid_data <- Area_Chennai_covid_data %>%filter(Zone %in% c(5) ) %>% ungroup()
Zone05_Chennai_covid_data$importDate<-as.Date(as.character(Zone05_Chennai_covid_data$importDate))

ggplot(Zone05_Chennai_covid_data
       ,aes(importDate, Area, fill= impactedStreets)) + 
  geom_tile(colour="white",size=0.25) +
  facet_grid(switch = "y", scales = "free_y", space = "free_y") +
  scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  ylab(label = "Area") +
  xlab(label = "Date") +
  scale_y_discrete(limits = rev(levels(as.factor(Zone05_Chennai_covid_data$Area ))) ) +
  theme_classic() +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m") +
  theme(strip.placement = "outside",
          plot.title = element_text(hjust = 0.5),
          axis.title.y = element_blank(), # Remove y-axis title
          strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
          legend.position="top"
      )

```
```{r echo=FALSE, warning=FALSE, message=FALSE, fig.height=10.5, fig.width=7}
ggplot(Zone05_Chennai_covid_data,aes(importDate, impactedStreets,fill=impactedStreets)) +
  geom_bar(stat="identity", color="white", fill="#e3e3e3") +
  geom_line(aes(importDate, impactedStreets), linetype=2, size=.3, color="black") +
  geom_ma(ma_fun = EMA, n = 7, linetype=1, color="blue") +
  scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  theme_classic() +
  xlab(label = "Date") +
  theme(strip.placement = "outside",
        plot.title = element_text(hjust = 0.5),
        axis.title.y = element_blank(), # Remove y-axis title
        strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        legend.position="top",
        panel.spacing.x = unit(4, "mm")
  ) +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m") +
  facet_wrap(~ Area, scales = "free_x", ncol = 3) +
  labs(subtitle = "7-day moving average") + theme(plot.subtitle=element_text(size=8, color="blue"))

```

###### [Back to full list of Zones](#loz) {style="float:right"}

## Zone 6 - Thiru. Vi. Ka. Nagar {#anchor06}
```{r echo=FALSE, warning=FALSE, fig.height=7, fig.width=7}
Zone06_Chennai_covid_data <- Area_Chennai_covid_data %>%filter(Zone %in% c(6) ) %>% ungroup()
Zone06_Chennai_covid_data$importDate<-as.Date(as.character(Zone06_Chennai_covid_data$importDate))

ggplot(Zone06_Chennai_covid_data
       ,aes(importDate, Area, fill= impactedStreets)) + 
  geom_tile(colour="white",size=0.25) +
  facet_grid(switch = "y", scales = "free_y", space = "free_y") +
  scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  ylab(label = "Area") +
  xlab(label = "Date") +
  scale_y_discrete(limits = rev(levels(as.factor(Zone06_Chennai_covid_data$Area ))) ) +
  theme_classic() +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m") +
  theme(strip.placement = "outside",
          plot.title = element_text(hjust = 0.5),
          axis.title.y = element_blank(), # Remove y-axis title
          strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
          legend.position="top"
      )

```
```{r echo=FALSE, warning=FALSE, message=FALSE, fig.height=8, fig.width=7}
ggplot(Zone06_Chennai_covid_data,aes(importDate, impactedStreets,fill=impactedStreets)) +
  geom_bar(stat="identity", color="white", fill="#e3e3e3") +
  geom_line(aes(importDate, impactedStreets), linetype=2, size=.3, color="black") +
  geom_ma(ma_fun = EMA, n = 7, linetype=1, color="blue") +  
  scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  theme_classic() +
  xlab(label = "Date") +
  theme(strip.placement = "outside",
        plot.title = element_text(hjust = 0.5),
        axis.title.y = element_blank(), # Remove y-axis title
        strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        legend.position="top",
        panel.spacing.x = unit(4, "mm")
  ) +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m") +
  facet_wrap(~ Area, scales = "free_x", ncol = 3) +
  labs(subtitle = "7-day moving average") + theme(plot.subtitle=element_text(size=8, color="blue"))

```

###### [Back to full list of Zones](#loz) {style="float:right"}

## Zone 7 - Ambattur {#anchor07}
```{r echo=FALSE, warning=FALSE, fig.height=10.5, fig.width=7}
Zone07_Chennai_covid_data <- Area_Chennai_covid_data %>%filter(Zone %in% c(7) ) %>% ungroup()
Zone07_Chennai_covid_data$importDate<-as.Date(as.character(Zone07_Chennai_covid_data$importDate))

ggplot(Zone07_Chennai_covid_data
       ,aes(importDate, Area, fill= impactedStreets)) + 
  geom_tile(colour="white",size=0.25) +
  facet_grid(switch = "y", scales = "free_y", space = "free_y") +
  scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  ylab(label = "Area") +
  xlab(label = "Date") +
  scale_y_discrete(limits = rev(levels(as.factor(Zone07_Chennai_covid_data$Area) )) ) +
  theme_classic() +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m") +
  theme(strip.placement = "outside",
          plot.title = element_text(hjust = 0.5),
          axis.title.y = element_blank(), # Remove y-axis title
          strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
          legend.position="top"
      )

```
```{r echo=FALSE, warning=FALSE, message=FALSE, fig.height=21, fig.width=7}
ggplot(Zone07_Chennai_covid_data,aes(importDate, impactedStreets,fill=impactedStreets)) +
  geom_bar(stat="identity", color="white", fill="#e3e3e3") +
  geom_line(aes(importDate, impactedStreets), linetype=2, size=.3, color="black") +
  geom_ma(ma_fun = EMA, n = 7, linetype=1, color="blue") +  
  scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  theme_classic() +
  xlab(label = "Date") +
  theme(strip.placement = "outside",
        plot.title = element_text(hjust = 0.5),
        axis.title.y = element_blank(), # Remove y-axis title
        strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        legend.position="top",
        panel.spacing.x = unit(4, "mm")
  ) +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m") +
  facet_wrap(~ Area, scales = "free_x", ncol = 3) +
  labs(subtitle = "7-day moving average") + theme(plot.subtitle=element_text(size=8, color="blue"))

```

###### [Back to full list of Zones](#loz) {style="float:right"}

## Zone 8 - Anna Nagar {#anchor08}
```{r echo=FALSE, warning=FALSE,fig.height=6, fig.width=7}
Zone08_Chennai_covid_data <- Area_Chennai_covid_data %>%filter(Zone %in% c(8) ) %>% ungroup()
Zone08_Chennai_covid_data$importDate<-as.Date(as.character(Zone08_Chennai_covid_data$importDate))

ggplot(Zone08_Chennai_covid_data
       ,aes(importDate, Area, fill= impactedStreets)) + 
  geom_tile(colour="white",size=0.25) +
  facet_grid(switch = "y", scales = "free_y", space = "free_y") +
  scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  ylab(label = "Area") +
  xlab(label = "Date") +
  scale_y_discrete(limits = rev(levels(as.factor(Zone08_Chennai_covid_data$Area ))) ) +
  theme_classic() +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m") +
  theme(strip.placement = "outside",
          plot.title = element_text(hjust = 0.5),
          axis.title.y = element_blank(), # Remove y-axis title
          strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
          legend.position="top"
      )

```
```{r echo=FALSE, warning=FALSE, message=FALSE, fig.height=8, fig.width=7}
ggplot(Zone08_Chennai_covid_data,aes(importDate, impactedStreets,fill=impactedStreets)) +
  geom_bar(stat="identity", color="white", fill="#e3e3e3") +
  geom_line(aes(importDate, impactedStreets), linetype=2, size=.3, color="black") +
  geom_ma(ma_fun = EMA, n = 7, linetype=1, color="blue") +  
  scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  theme_classic() +
  xlab(label = "Date") +
  theme(strip.placement = "outside",
        plot.title = element_text(hjust = 0.5),
        axis.title.y = element_blank(), # Remove y-axis title
        strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        legend.position="top",
        panel.spacing.x = unit(4, "mm")
  ) +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m") +
  facet_wrap(~ Area, scales = "free_x", ncol = 3) +
  labs(subtitle = "7-day moving average") + theme(plot.subtitle=element_text(size=8, color="blue"))

```

###### [Back to full list of Zones](#loz) {style="float:right"}

## Zone 9 - Teynampet {#anchor09}
```{r echo=FALSE, warning=FALSE, fig.height=6, fig.width=7}
Zone09_Chennai_covid_data <- Area_Chennai_covid_data %>%filter(Zone %in% c(9) ) %>% ungroup()
Zone09_Chennai_covid_data$importDate<-as.Date(as.character(Zone09_Chennai_covid_data$importDate))

ggplot(Zone09_Chennai_covid_data
       ,aes(importDate, Area, fill= impactedStreets)) + 
  geom_tile(colour="white",size=0.25) +
  facet_grid(switch = "y", scales = "free_y", space = "free_y") +
  scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  ylab(label = "Area") +
  xlab(label = "Date") +
  scale_y_discrete(limits = rev(levels(as.factor(Zone09_Chennai_covid_data$Area) ))) +
  theme_classic() +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m") +
  theme(strip.placement = "outside",
          plot.title = element_text(hjust = 0.5),
          axis.title.y = element_blank(), # Remove y-axis title
          strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
          legend.position="top"
      )

```
```{r echo=FALSE, warning=FALSE, message=FALSE, fig.height=10, fig.width=7}
ggplot(Zone09_Chennai_covid_data,aes(importDate, impactedStreets,fill=impactedStreets)) +
  geom_bar(stat="identity", color="white", fill="#e3e3e3") +
  geom_line(aes(importDate, impactedStreets), linetype=2, size=.3, color="black") +
  geom_ma(ma_fun = EMA, n = 7, linetype=1, color="blue") +  
  scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  theme_classic() +
  xlab(label = "Date") +
  theme(strip.placement = "outside",
        plot.title = element_text(hjust = 0.5),
        axis.title.y = element_blank(), # Remove y-axis title
        strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        legend.position="top",
        panel.spacing.x = unit(4, "mm")
  ) +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m") +
  facet_wrap(~ Area, scales = "free_x", ncol = 3) +
  labs(subtitle = "7-day moving average") + theme(plot.subtitle=element_text(size=8, color="blue"))

```

###### [Back to full list of Zones](#loz) {style="float:right"}

## Zone 10 - Kodambakkam {#anchor10}
```{r echo=FALSE, warning=FALSE, fig.height=7, fig.width=7}
Zone10_Chennai_covid_data <- Area_Chennai_covid_data %>%filter(Zone %in% c(10) ) %>% ungroup()
Zone10_Chennai_covid_data$importDate<-as.Date(as.character(Zone10_Chennai_covid_data$importDate))

ggplot(Zone10_Chennai_covid_data
       ,aes(importDate, Area, fill= impactedStreets)) + 
  geom_tile(colour="white",size=0.25) +
  facet_grid(switch = "y", scales = "free_y", space = "free_y") +
  scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  ylab(label = "Area") +
  xlab(label = "Date") +
  scale_y_discrete(limits = rev(levels(as.factor(Zone10_Chennai_covid_data$Area) ))) +
  theme_classic() +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m") +
  theme(strip.placement = "outside",
          plot.title = element_text(hjust = 0.5),
          axis.title.y = element_blank(), # Remove y-axis title
          strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
          legend.position="top"
      )

```
```{r echo=FALSE, warning=FALSE, message=FALSE, fig.height=8, fig.width=7}
ggplot(Zone10_Chennai_covid_data,aes(importDate, impactedStreets,fill=impactedStreets)) +
  geom_bar(stat="identity", color="white", fill="#e3e3e3") +
  geom_line(aes(importDate, impactedStreets), linetype=2, size=.3, color="black") +
  geom_ma(ma_fun = EMA, n = 7, linetype=1, color="blue") +  
  scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  theme_classic() +
  xlab(label = "Date") +
  theme(strip.placement = "outside",
        plot.title = element_text(hjust = 0.5),
        axis.title.y = element_blank(), # Remove y-axis title
        strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        legend.position="top",
        panel.spacing.x = unit(4, "mm")
  ) +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m") +
  facet_wrap(~ Area, scales = "free_x", ncol = 3) +
  labs(subtitle = "7-day moving average") + theme(plot.subtitle=element_text(size=8, color="blue"))

```

###### [Back to full list of Zones](#loz) {style="float:right"}

## Zone 11 - Valasaravakkam {#anchor11}
```{r echo=FALSE, warning=FALSE}
Zone11_Chennai_covid_data <- Area_Chennai_covid_data %>%filter(Zone %in% c(11) ) %>% ungroup()
Zone11_Chennai_covid_data$importDate<-as.Date(as.character(Zone11_Chennai_covid_data$importDate))

ggplot(Zone11_Chennai_covid_data
       ,aes(importDate, Area, fill= impactedStreets)) + 
  geom_tile(colour="white",size=0.25) +
  facet_grid(switch = "y", scales = "free_y", space = "free_y") +
  scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  ylab(label = "Area") +
  xlab(label = "Date") +
  scale_y_discrete(limits = rev(levels(as.factor(Zone11_Chennai_covid_data$Area) ))) +
  theme_classic() +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m") +
  theme(strip.placement = "outside",
          plot.title = element_text(hjust = 0.5),
          axis.title.y = element_blank(), # Remove y-axis title
          strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
          legend.position="top"
      )

```
```{r echo=FALSE, warning=FALSE, message=FALSE, fig.height=7, fig.width=7}
ggplot(Zone11_Chennai_covid_data,aes(importDate, impactedStreets,fill=impactedStreets)) +
  geom_bar(stat="identity", color="white", fill="#e3e3e3") +
  geom_line(aes(importDate, impactedStreets), linetype=2, size=.3, color="black") +
  geom_ma(ma_fun = EMA, n = 7, linetype=1, color="blue") +  
  scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  theme_classic() +
  xlab(label = "Date") +
  theme(strip.placement = "outside",
        plot.title = element_text(hjust = 0.5),
        axis.title.y = element_blank(), # Remove y-axis title
        strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        legend.position="top",
        panel.spacing.x = unit(4, "mm")
  ) +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m") +
  facet_wrap(~ Area, scales = "free_x", ncol = 3) +
  labs(subtitle = "7-day moving average") + theme(plot.subtitle=element_text(size=8, color="blue"))

```

###### [Back to full list of Zones](#loz) {style="float:right"}

## Zone 12 - Alandur {#anchor12}
```{r echo=FALSE, warning=FALSE}
Zone12_Chennai_covid_data <- Area_Chennai_covid_data %>%filter(Zone %in% c(12) ) %>% ungroup()
Zone12_Chennai_covid_data$importDate<-as.Date(as.character(Zone12_Chennai_covid_data$importDate))

ggplot(Zone12_Chennai_covid_data
       ,aes(importDate, Area, fill= impactedStreets)) + 
  geom_tile(colour="white",size=0.25) +
  facet_grid(switch = "y", scales = "free_y", space = "free_y") +
  scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  ylab(label = "Area") +
  xlab(label = "Date") +
  scale_y_discrete(limits = rev(levels(as.factor(Zone12_Chennai_covid_data$Area) ))) +
  theme_classic() +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m") +
  theme(strip.placement = "outside",
          plot.title = element_text(hjust = 0.5),
          axis.title.y = element_blank(), # Remove y-axis title
          strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
          legend.position="top"
      )

```
```{r echo=FALSE, warning=FALSE, message=FALSE, fig.height=8, fig.width=7}
ggplot(Zone12_Chennai_covid_data,aes(importDate, impactedStreets,fill=impactedStreets)) +
  geom_bar(stat="identity", color="white", fill="#e3e3e3") +
  geom_line(aes(importDate, impactedStreets), linetype=2, size=.3, color="black") +
  geom_ma(ma_fun = EMA, n = 7, linetype=1, color="blue") +  
  scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  theme_classic() +
  xlab(label = "Date") +
  theme(strip.placement = "outside",
        plot.title = element_text(hjust = 0.5),
        axis.title.y = element_blank(), # Remove y-axis title
        strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        legend.position="top",
        panel.spacing.x = unit(4, "mm")
  ) +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m") +
  facet_wrap(~ Area, scales = "free_x", ncol = 3) +
  labs(subtitle = "7-day moving average") + theme(plot.subtitle=element_text(size=8, color="blue"))

```

###### [Back to full list of Zones](#loz) {style="float:right"}

## Zone 13 - Adyar {#anchor13}
```{r echo=FALSE, warning=FALSE, fig.height=7, fig.width=7}
Zone13_Chennai_covid_data <- Area_Chennai_covid_data %>%filter(Zone %in% c(13) ) %>% ungroup()
Zone13_Chennai_covid_data$importDate<-as.Date(as.character(Zone13_Chennai_covid_data$importDate))

ggplot(Zone13_Chennai_covid_data
       ,aes(importDate, Area, fill= impactedStreets)) + 
  geom_tile(colour="white",size=0.25) +
  facet_grid(switch = "y", scales = "free_y", space = "free_y") +
  scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  ylab(label = "Area") +
  xlab(label = "Date") +
  scale_y_discrete(limits = rev(levels(as.factor(Zone13_Chennai_covid_data$Area) ))) +
  theme_classic() +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m") +
  theme(strip.placement = "outside",
          plot.title = element_text(hjust = 0.5),
          axis.title.y = element_blank(), # Remove y-axis title
          strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
          legend.position="top"
      )
```
```{r echo=FALSE, warning=FALSE, message=FALSE, fig.height=11, fig.width=7}
ggplot(Zone13_Chennai_covid_data,aes(importDate, impactedStreets,fill=impactedStreets)) +
  geom_bar(stat="identity", color="white", fill="#e3e3e3") +
  geom_line(aes(importDate, impactedStreets), linetype=2, size=.3, color="black") +
  geom_ma(ma_fun = EMA, n = 7, linetype=1, color="blue") +  
  scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  theme_classic() +
  xlab(label = "Date") +
  theme(strip.placement = "outside",
        plot.title = element_text(hjust = 0.5),
        axis.title.y = element_blank(), # Remove y-axis title
        strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        legend.position="top",
        panel.spacing.x = unit(4, "mm")
  ) +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m") +
  facet_wrap(~ Area, scales = "free_x", ncol = 3) +
  labs(subtitle = "7-day moving average") + theme(plot.subtitle=element_text(size=8, color="blue"))

```

###### [Back to full list of Zones](#loz) {style="float:right"}

## Zone 14 - Perungudi {#anchor14}
```{r echo=FALSE, warning=FALSE}
Zone14_Chennai_covid_data <- Area_Chennai_covid_data %>%filter(Zone %in% c(14) ) %>% ungroup()
Zone14_Chennai_covid_data$importDate<-as.Date(as.character(Zone14_Chennai_covid_data$importDate))

ggplot(Zone14_Chennai_covid_data
       ,aes(importDate, Area, fill= impactedStreets)) + 
  geom_tile(colour="white",size=0.25) +
  facet_grid(switch = "y", scales = "free_y", space = "free_y") +
  scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  ylab(label = "Area") +
  xlab(label = "Date") +
  scale_y_discrete(limits = rev(levels(as.factor(Zone14_Chennai_covid_data$Area) ))) +
  theme_classic() +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m") +
  theme(strip.placement = "outside",
          plot.title = element_text(hjust = 0.5),
          axis.title.y = element_blank(), # Remove y-axis title
          strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
          legend.position="top"
      )
```
```{r echo=FALSE, warning=FALSE, message=FALSE, fig.height=7, fig.width=7}
ggplot(Zone14_Chennai_covid_data,aes(importDate, impactedStreets,fill=impactedStreets)) +
  geom_bar(stat="identity", color="white", fill="#e3e3e3") +
  geom_line(aes(importDate, impactedStreets), linetype=2, size=.3, color="black") +
  geom_ma(ma_fun = EMA, n = 7, linetype=1, color="blue") +  
  scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  theme_classic() +
  xlab(label = "Date") +
  theme(strip.placement = "outside",
        plot.title = element_text(hjust = 0.5),
        axis.title.y = element_blank(), # Remove y-axis title
        strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        legend.position="top",
        panel.spacing.x = unit(4, "mm")
  ) +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m") +
  facet_wrap(~ Area, scales = "free_x", ncol = 3) +
  labs(subtitle = "7-day moving average") + theme(plot.subtitle=element_text(size=8, color="blue"))

```

###### [Back to full list of Zones](#loz) {style="float:right"}

## Zone 15 - Sholinganallur {#anchor15}
```{r echo=FALSE, warning=FALSE}
Zone15_Chennai_covid_data <- Area_Chennai_covid_data %>%filter(Zone %in% c(15) ) %>% ungroup()
Zone15_Chennai_covid_data$importDate<-as.Date(as.character(Zone15_Chennai_covid_data$importDate))

ggplot(Zone15_Chennai_covid_data
       ,aes(importDate, Area, fill= impactedStreets)) + 
  geom_tile(colour="white",size=0.25) +
  facet_grid(switch = "y", scales = "free_y", space = "free_y") +
  scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  ylab(label = "Area") +
  xlab(label = "Date") +
  scale_y_discrete(limits = rev(levels(as.factor(Zone15_Chennai_covid_data$Area) ))) +
  theme_classic() +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m") +
  theme(strip.placement = "outside",
          plot.title = element_text(hjust = 0.5),
          axis.title.y = element_blank(), # Remove y-axis title
          strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
          legend.position="top"
      )
```
```{r echo=FALSE, warning=FALSE, message=FALSE, fig.height=7, fig.width=7}
ggplot(Zone15_Chennai_covid_data,aes(importDate, impactedStreets,fill=impactedStreets)) +
  geom_bar(stat="identity", color="white", fill="#e3e3e3") +
  geom_line(aes(importDate, impactedStreets), linetype=2, size=.3, color="black") +
  geom_ma(ma_fun = EMA, n = 7, linetype=1, color="blue") +  
  scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  theme_classic() +
  xlab(label = "Date") +
  theme(strip.placement = "outside",
        plot.title = element_text(hjust = 0.5),
        axis.title.y = element_blank(), # Remove y-axis title
        strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        legend.position="top",
        panel.spacing.x = unit(4, "mm")
  ) +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m") +
  facet_wrap(~ Area, scales = "free_x", ncol = 3) +
  labs(subtitle = "7-day moving average") + theme(plot.subtitle=element_text(size=8, color="blue"))

```

###### [Back to full list of Zones](#loz) {style="float:right"}